Perceptions and Preferences for Meritocracy Scale (PPM-S)

### 2020-01-13 index.Rmd
update1301-2010

---
title: "Perceptions and Preferences for Meritocracy Scale (PPM-S)"
csl: "input/bib/apa6.csl"
bibliography: "input/bib/zlibrary.bib"
css: tyle.css
output:
  pdf_document:
    keep_tex: false
    template: null
    number_sections: true
    toc: true
  html_document:
    theme: flatly
    number_sections: true
    toc: true
    toc_float: true
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
linestretch: '1.5'
link-citations: yes
linkcolor: blue
---

>>>>

---
title: "Perceptions and Preferences for Meritocracy Scale (PPM-S)"
csl: "input/bib/apa6.csl"
bibliography: "input/bib/zlibrary.bib"
css: style.css
output:
  pdf_document:
    keep_tex: false
    template: null
    number_sections: true
    toc: true
  html_document:
    theme: flatly
    number_sections: true
    toc: true
    toc_float: true
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
linestretch: '1.5'
link-citations: yes
linkcolor: blue
---
